Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-18 analysis/paper/Rmd/hotspot-one-chromosome.Rmd
removed code for working with blups

```{r, readRDS-{{hot_chr}}}
pleio_mixed_list <- readRDS(here("analysis", "data", "derived_data", paste0("Chr", {{hot_chr}}, "_pleio.rds")))
pleio_local_list <- readRDS(here("analysis", "data", "derived_data", paste0("Chr", {{hot_chr}}, "_pleio_local.rds")))
pleio_nonlocal_list <- readRDS(here("analysis", "data", "derived_data", paste0("Chr", {{hot_chr}}, "_pleio_nonlocal.rds")))
med_list <- readRDS(here("analysis", "data", "derived_data", paste0("Chr", {{hot_chr}}, "_mediations.rds")))
```

@@

```{r, get-allele-effects-{{hot_chr}}}
# add index values for peak position
local_nonlocal_annot <- dplyr::bind_rows(local_annot2, nonlocal_annot) %>%
  mutate(peak_index = match(table = names(map[["{{hot_chr}}"]]), x = marker.id)) %>%
  mutate(peak_effects = purrr::map2(.f = qtl2pleio::get_effects, .x = peak_index, .y = s1coef_out, map = map[["{{hot_chr}}"]])) %>%
  qtl2hotspots::listcol_to_cols(list_column = quo(peak_effects), another_column = quo(symbol))
```

@@

```{r, order-annotations-{{hot_chr}}}
# all annots 
annots_ord <- list(lod_diffs_tibble, 
                   lod_diff_proportions_tibble, 
                   allele_effects_tibble,
                   peak_positions, 
                   local_tibble,
                   lod_tibble
                    ) %>% 
  purrr::map(.f = function(df, rn){
    out <- df[match(x = rn, table = df$symbol), ]
    return(out)
  }, 
  rn = rn)
```

@@

```{r iheatmapr-{{hot_chr}}, out.width="25in", out.height = "10in"}
ann3 <- annots_ord[[3]] %>%
  ungroup() %>%
  select(- symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[3]]$symbol; return(x)})
colnames(ann3) <- LETTERS[1:8]
ann2 <- annots_ord[[2]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[2]]$symbol; return(x)})
ann1 <- annots_ord[[1]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[1]]$symbol; return(x)})
ann5 <- annots_ord[[5]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[5]]$symbol; return(x)})
ann6 <- annots_ord[[6]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[6]]$symbol; return(x)})
ann4 <- annots_ord[[4]] %>%
  ungroup() %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[4]]$symbol; return(x)})
mymat <- pm[ord, ord] %>% # order both cols and rows by 'ord'
  apply(FUN = trunc2, MARGIN = 2, threshold = 5)
iheatmapr::main_heatmap(mymat, show_colorbar = FALSE, layout = list(font = list(size = 4))) %>%
  iheatmapr::add_col_labels() %>%
  iheatmapr::add_col_annotation(ann5) %>%
  iheatmapr::add_main_heatmap(ann3, name = "signal3", size = 0.2, show_colorbar = FALSE) %>%
    iheatmapr::add_col_labels() %>%

  iheatmapr::add_main_heatmap(ann2, name = "signal2", size = 0.5, show_colorbar = FALSE) %>%
  iheatmapr::add_col_labels() %>%
  iheatmapr::add_main_heatmap(ann1, name = "signal1", size = 0.5, show_colorbar = FALSE) %>%
  iheatmapr::add_row_annotation(ann5, side = "left") %>%
    iheatmapr::add_col_labels() %>%
  iheatmapr::add_row_annotation(ann4, side = "left") %>%
  iheatmapr::add_row_annotation(ann6, side = "left") %>%
    iheatmapr::add_row_labels()

>>>>

```{r, readRDS-{{hot_chr}}}
pleio_mixed_list <- readRDS(here::here("analysis", "data", "derived_data", paste0("Chr", {{hot_chr}}, "_pleio.rds")))
pleio_local_list <- readRDS(here::here("analysis", "data", "derived_data", paste0("Chr", {{hot_chr}}, "_pleio_local.rds")))
pleio_nonlocal_list <- readRDS(here::here("analysis", "data", "derived_data", paste0("Chr", {{hot_chr}}, "_pleio_nonlocal.rds")))
med_list <- readRDS(here::here("analysis", "data", "derived_data", paste0("Chr", {{hot_chr}}, "_mediations.rds")))
```

@@

```{r, get-allele-effects-{{hot_chr}}}
# add index values for peak position
local_nonlocal_annot <- dplyr::bind_rows(local_annot2, nonlocal_annot) %>%
  mutate(peak_index = match(table = names(map[["{{hot_chr}}"]]), x = marker.id)) %>%
  mutate(peak_effects = purrr::map2(.f = qtl2pleio::get_effects, .x = peak_index, .y = s1coef_out, map = map[["{{hot_chr}}"]])) %>%
  qtl2hotspots::listcol_to_cols(list_column = quo(peak_effects), another_column = quo(symbol)) %>%
  rename(cA = `1`, cB = `2`, cC = `3`, cD = `4`, cE = `5`, cF = `6`, cG = `7`, cH = `8`
         ) %>%
```

```{r, define-contrasts-{{hot_chr}}}
contrasts_BC_FG <- local_nonlocal_annot %>%
  ungroup() %>%
  select(symbol, cA:cH, local_tx, lod) %>%
  (function(x) x[ord2, ]) %>%
  mutate(row_num = 1:nrow(local_nonlocal_annot), 
         AB = abs(cA - cB),
         AC = abs(cA - cC),
         AD = abs(cA - cD),
         AE = abs(cA - cE),
         AF = abs(cA - cF),
         AG = abs(cA - cG),
         AH = abs(cA - cH),
         BC = abs(cB - cC),
         BD = abs(cB - cD),
         BE = abs(cB - cE),
         BF = abs(cB - cF),
         BG = abs(cB - cG),
         BH = abs(cB - cH),
         CD = abs(cC - cD),
         CE = abs(cC - cE),
         CF = abs(cC - cF),
         CG = abs(cC - cG),
         CH = abs(cC - cH),
         DE = abs(cD - cE),
         DF = abs(cD - cF),
         DG = abs(cD - cG),
         DH = abs(cD - cH),
         EF = abs(cE - cF),
         EG = abs(cE - cG),
         EH = abs(cE - cH),
         FG = abs(cF - cG),
         FH = abs(cF - cH),
         GH = abs(cG - cH)
  ) %>%
  mutate(BC_A = abs((cB + cC) / 2 - cA),
         BC_D = abs((cB + cC) / 2 - cD),
         BC_E = abs((cB + cC) / 2 - cE),
         BC_F = abs((cB + cC) / 2 - cF),
         BC_G = abs((cB + cC) / 2 - cG),
         BC_H = abs((cB + cC) / 2 - cH),
         BC_FG = abs((cB + cC) - (cF + cG))
         ) %>%
  select(symbol, BC_FG)

@@

```{r, order-annotations-{{hot_chr}}}
# all annots 
annots_ord <- list(lod_diffs_tibble, 
                   lod_diff_proportions_tibble, 
                   allele_effects_tibble,
                   peak_positions, 
                   local_tibble,
                   lod_tibble, 
                   contrasts_BC_FG
                    ) %>% 
  purrr::map(.f = function(df, rn){
    out <- df[match(x = rn, table = df$symbol), ]
    return(out)
  }, 
  rn = rn)
```

@@

```{r iheatmapr-{{hot_chr}}, out.width="25in", out.height = "10in"}
ann3 <- annots_ord[[3]] %>%
  ungroup() %>%
  select(- symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[3]]$symbol; return(x)})
colnames(ann3) <- LETTERS[1:8]
ann2 <- annots_ord[[2]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[2]]$symbol; return(x)})
ann1 <- annots_ord[[1]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[1]]$symbol; return(x)})
ann5 <- annots_ord[[5]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[5]]$symbol; return(x)})
ann6 <- annots_ord[[6]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[6]]$symbol; return(x)})
ann7 <- annots_ord[[7]] %>% # BC_FG contrast
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[7]]$symbol; return(x)})
ann4 <- annots_ord[[4]] %>%
  ungroup() %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[4]]$symbol; return(x)})
mymat <- pm[ord, ord] %>% # order both cols and rows by 'ord'
  apply(FUN = trunc2, MARGIN = 2, threshold = 5)
iheatmapr::main_heatmap(mymat, show_colorbar = FALSE, layout = list(font = list(size = 4))) %>%
  iheatmapr::add_col_labels() %>%
  iheatmapr::add_col_annotation(ann5) %>%
  iheatmapr::add_main_heatmap(ann3, name = "signal3", size = 0.2, show_colorbar = FALSE) %>%
    iheatmapr::add_col_labels() %>%

  iheatmapr::add_main_heatmap(ann2, name = "signal2", size = 0.5, show_colorbar = FALSE) %>%
  iheatmapr::add_col_labels() %>%
  iheatmapr::add_main_heatmap(ann1, name = "signal1", size = 0.5, show_colorbar = FALSE) %>%
  iheatmapr::add_row_annotation(ann5, side = "left") %>%
    iheatmapr::add_col_labels() %>%
  iheatmapr::add_row_annotation(ann4, side = "left") %>%
  iheatmapr::add_row_annotation(ann6, side = "left") %>%
  iheatmapr::add_row_annotation(ann7, side = "left") %>%
  iheatmapr::add_row_labels()

### 2019-08-18 analysis/paper/Rmd/hotspots-paper.Rmd
switched to eval = TRUE for git2r code
removed code for working with blups

```{r load-broman}
library(broman)
library(here)
```

@@

```{r setup}
library(knitr)
library(qtl2hotspots)
ult <- 15 # univariate lod threshold
```

@@

```{r saveRDS}
if (!file.exists(here("analysis", "data", "derived_data", "genoprobs.rds"))){
  download.file("https://datadryad.org/bitstream/handle/10255/dryad.166774/Attie_DO378_eQTL_viewer_v1.Rdata?sequence=2",
              destfile = here("analysis", "data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata")
              )
  load(here("analysis", "data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata"))
  saveRDS(dataset.islet.rnaseq$lod.peaks, here("analysis", "data", "derived_data", "lod_peaks.rds"))
  saveRDS(dataset.islet.rnaseq$annots, here("analysis", "data", "derived_data", "annots.rds"))
  saveRDS(dataset.islet.rnaseq$expr, here("analysis", "data", "derived_data", "expr.rds"))
  saveRDS(K, here("analysis", "data", "derived_data", "kinship.rds"))
  saveRDS(map, here("analysis", "data", "derived_data", "map.rds"))
  saveRDS(genoprobs, here("analysis", "data", "derived_data", "genoprobs.rds"))
  saveRDS(dataset.islet.rnaseq$covar, here("analysis", "data", "derived_data", "covar.rds"))
}
```

```{r readRDS}
lod_peaks <- readRDS(here("analysis", "data", "derived_data", "lod_peaks.rds"))
annots <- readRDS(here("analysis", "data", "derived_data", "annots.rds"))
expr <- readRDS(here("analysis", "data", "derived_data", "expr.rds"))
probs <- readRDS(here("analysis", "data", "derived_data", "genoprobs.rds"))
K <- readRDS(here("analysis", "data", "derived_data", "kinship.rds"))
covar <- readRDS(here("analysis", "data", "derived_data", "covar.rds"))
map <- readRDS(here("analysis", "data", "derived_data", "map.rds"))
```

@@

```{r git2r, cache = FALSE, echo = TRUE, eval = FALSE}
# what commit is this file at?
git2r::repository(here::here())
```

>>>>

@@

```{r setup}
library(qtl2hotspots)
ult <- 15 # univariate lod threshold
```

@@

```{r saveRDS}
if (!file.exists(here::here("analysis", "data", "derived_data", "genoprobs.rds"))){
  download.file("https://datadryad.org/bitstream/handle/10255/dryad.166774/Attie_DO378_eQTL_viewer_v1.Rdata?sequence=2",
              destfile = here::here("analysis", "data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata")
              )
  load(here::here("analysis", "data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata"))
  saveRDS(dataset.islet.rnaseq$lod.peaks, here::here("analysis", "data", "derived_data", "lod_peaks.rds"))
  saveRDS(dataset.islet.rnaseq$annots, here::here("analysis", "data", "derived_data", "annots.rds"))
  saveRDS(dataset.islet.rnaseq$expr, here::here("analysis", "data", "derived_data", "expr.rds"))
  saveRDS(K, here::here("analysis", "data", "derived_data", "kinship.rds"))
  saveRDS(map, here::here("analysis", "data", "derived_data", "map.rds"))
  saveRDS(genoprobs, here::here("analysis", "data", "derived_data", "genoprobs.rds"))
  saveRDS(dataset.islet.rnaseq$covar, here::here("analysis", "data", "derived_data", "covar.rds"))
}
```

```{r readRDS}
lod_peaks <- readRDS(here::here("analysis", "data", "derived_data", "lod_peaks.rds"))
annots <- readRDS(here::here("analysis", "data", "derived_data", "annots.rds"))
expr <- readRDS(here::here("analysis", "data", "derived_data", "expr.rds"))
probs <- readRDS(here::here("analysis", "data", "derived_data", "genoprobs.rds"))
K <- readRDS(here::here("analysis", "data", "derived_data", "kinship.rds"))
covar <- readRDS(here::here("analysis", "data", "derived_data", "covar.rds"))
map <- readRDS(here::here("analysis", "data", "derived_data", "map.rds"))
```

@@

```{r git2r, cache = FALSE, echo = TRUE, eval = TRUE}
# what commit is this file at?
git2r::repository(here::here())
```
